Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-09 Geometric types.tex
Talking with  David

In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.

@@

%\item 
Let $\CS_{G\der}(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$.
%Thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
Morphisms in $\CS_{G\der}(G)$ are morphisms in $\CS(G)$ commuting with $\nu$. 
%\end{itemize}

>>>>

Let $q : G\to G\ab$ be the quotient
In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.

@@

Suppose $\cs{L}\ab\in \Loc(G\ab)$.
The local system $q^*\cs{L}\ab \in \Loc(G)$ is equivariant, for $\nu : n^*q^*\cs{L}\ab\to p^*q^*\cs{L}\ab$ defined by

%\item 
Let $\CS_{\text{eq}}(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$.
%Thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
Morphisms in $\CS_{G\der}(G)$ are morphisms in $\CS(G)$ commuting with $\nu$. 
%\end{itemize}
